\documentclass[10pt]{article}

\usepackage{cite}

\begin{document}

\section{Introduction}

The social media website Reddit is a popular destination for internet users. The site's popularity has grown dramatically since its inception nearly fifteen years ago; in 2013, Duggan et al.\ showed that six percent of online adults use Reddit~\cite{pewsixpercent}.

Reddit is organized into user-controlled subcommunities called \textit{subreddits}. Any user can create a subreddit; the name of the subreddit dictates the general content found in it. By convention, subreddits are prefixed with \textit{r/ or /r/}, which reflects the URL used to access it. For example, the subreddit \textit{/r/games} is about video games in general, but there are also game-specific subreddits such as \textit{/r/dota2} for discussion about a specific video game. Users can \textit{subscribe} to subreddits to view their posts in the user's personalized frontpage feed.

Content posted to Reddit takes the form of \textit{posts}, which resemble traditional forum threads. Subreddits are \textit{moderated} by users; they have the authority to curate user-submitted posts.

Reddit users are pseudonymous; they are identified only by their username and the content they post on the website. Public user data includes a user's comments, submitted posts, and which posts they have upvoted and downvoted~\cite{redditapi}. Together, this data provides a publicly-visible \textit{behavioral profile} of users on the site.

Prior work has shown, using the social media website Twitter, that users are identifiable when correlating browser history with links found in personalized Twitter feeds~\cite{su2017deanonymizingweb}. Users can also be de-anonymized when linking their profiles across multiple sites~\cite{}\cite{}.

This prior work shows that users on social media websites still have identifiable behavioral patterns, and in the case of Twitter, often identifiable enough to successfully de-anonymize users.

Our work, however, does not concern de-anonymization, but rather it involves \textit{prediction}. The question we are trying to answer has two components.

First of all, do Reddit users who are active on niche subreddits exhibit different posting, commenting, and voting behaviors than the average user?

Secondly, if the above is true, if a given user is not active in a particular niche subreddit, but their behavioral profile is similar to those of users active in that subreddit, are they more likely to become active in that subreddit in the future than the average population is?

\section{Experimental Design}

\bibliography{bib}
\bibliographystyle{plain}

\end{document}

